Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models

### 2020-12-02 analysis/paper/paper.Rmd
made the font size 10 in all tables in main document and appendix

---
title: "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    bookdown::pdf_document2:
      fig_caption: yes
      number_sections: false
      toc: no
      geometry: margin=1in
      latex_engine: "xelatex"
      keep_tex: true
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
      includes:
        in_header: ../templates/header_manuscript.tex
    bookdown::html_document2:
      fig_caption: yes
      number_sections: false
      toc: no
      fig_width: 7
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      # reference_docx: "../templates/EcologicalApplicationsTemplate.docx" # Insert path for the DOCX file
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: false
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
abstract: |
  Establishing robust methods and metrics to evaluate habitat quality is critical for the recovery of endangered Pacific salmonids. A variety of modeling approaches are used for status and trend monitoring of anadromous species throughout the Pacific Northwest, USA, but current methods may fail to capture the complex relationship between fish and habitat and are often limited in predictive power beyond specific watersheds. Further, the focus on species distribution and abundance is not easily manipulated to predict carrying capacity and traditional stock-recruitment analyses are reliant on long-term data which are not always available. In this study, we developed a quantile random forest (QRF) model to  provide estimates of habitat carrying capacity for Chinook salmon parr during the summer months, at both the site and watershed scale. QRF models allow for the consideration of noisy data, correlated variables, and non-linear relationships: common features in fish-habitat datasets. We leveraged Columbia Habitat Monitoring Program (CHaMP) data to select habitat co-variates and predict capacity at those sites. We also identified a set of globally available attributes to extrapolate capacity estimate predictions throughout wadeable streams within the Columbia River basin. Total capacity estimates for watersheds closely matched estimates from alternative fish productivity models. Carrying capacity estimates based on QRF, like those presented here, provide managers a framework to guide the identification, prioritization, and development of habitat rehabilitation actions to recover salmon populations.
keywords: |
  carrying capacity; quantile regression; random forests; Chinook; quantile random forest
highlights: |
  These are the highlights. 
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("pdf", "png", 'tiff'),
  dpi = 400
)
```

@@

Most studies that have investigated fish-habitat relationships focus on predicting a species’ distribution (presence / absence) or the average abundance or density: neither of which can be easily manipulated to predict carrying capacity. Further, many of these studies focus on only one or two measures of habitat. @Fausch1988 conducted a thorough review of attempts to predict the abundance of fish from measurable habitat covariates from 1950 to 1985 and found that the vast majority of multiple linear regression models failed to detect a significant fish-habitat signal. Since that review, there has been progress in identifying some fish-habitat relationships for several salmonid species. @Nickelson1992 demonstrated that juvenile coho salmon (*O. kisutch*) were found in higher densities within pool habitat on the Oregon coast. Similarly, pool and pond densities were good predictors of coho smolt densities in western Washington [@Sharma2001]. @Bryant2009 found that juvenile coho abundance was positively related to large wood at the reach scale; however their results demonstrated a negative relationship between abundance and the number of pools. @Braun2011 similarly found positive associations between spawner densities of sockeye salmon (*O. nerka*) in the Fraser River and large wood, in addition to positive relationships to percent undercuts and percent pools. Densities of adult spawning coho were also higher in forested areas compared to urban or agricultural areas in the Snohomish River watershed [@Pess2002]. @Mossop2006 examined juvenile Chinook salmon (*O. tshawytscha*) in the Yukon River and found positive correlations between the log of fish density and several metrics related to residual pool dimensions and large woody debris abundance as well as a negative correlation between fish density and gradient. These studies were focused on predicting observed fish densities, not necessarily capacity, and for most of them the predictive extent is limited to a particular watershed. In addition, they all assumed some form of linear fish-habitat relationship which often results in weak predictive power.

@@

```{r fish-hab-sites}
qrf_data %>%
  tabyl(Watershed) %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  rename(`n Sites` = n,
         Percent = percent) %>%
  kable(caption = 'The number of unique sites, by watershed, with paired fish-habitat data used to populate the spring/summer-run Chinook salmon parr capacity QRF model',
        booktabs = T,
        linesep = "") %>%
  kable_styling(latex_options = c("hold_position"))

@@

```{r select-mets-table, eval = T}
qrf_mod$importance %>%
  as_tibble(rownames = 'ShortName') %>%
  rename(imp = IncNodePurity) %>%
  arrange(desc(imp)) %>%
  mutate(Rank = 1:n()) %>%
  select(-imp) %>%
  left_join(hab_dict %>%
              select(-Name) %>%
              inner_join(sel_hab_mets %>%
                           rename(ShortName = Metric)) %>%
              mutate(Name = str_replace(Name, '\n', ' '))) %>%
  filter(MetricGroupName != 'Tier 1 Summary') %>%
  select(Rank,
         Metric = Name,
         `Metric Category` = MetricCategory,
         Description = DescriptiveText) %>%
  kable(caption = "Habitat metrics and descriptions of metrics included in the QRF model to predict spring/summer-run Chinook salmon parr capacity. Metrics are ranked in order of relative importance.",
        booktabs = T,
        linesep = "",
        format.args = list(width = c(2, 10, 10, 50))) %>%
  kable_styling(latex_options = c("hold_position")) %>%
  column_spec(4, width = '3in')

@@

```{r gaa-covars, eval = T}
tibble(Covariate = gaa_covars) %>%
  left_join(gaa_meta %>%
              select(Covariate = FieldName,
                     Name = DisplayName,
                     Units,
                     SpatialScale)) %>%
  mutate(Units = if_else(Units == "na",
                         as.character(NA),
                         Units),
         Units = if_else(grepl('\\^2', Units),
                         str_replace(Units, '\\^2', '$^2$'),
                         Units)) %>%
  mutate(Name = if_else(Covariate == 'S2_02_11' & is.na(Name),
                        'NorWeST Aug. Temperature',
                        Name),
         Units = if_else(Covariate == 'S2_02_11',
                                'C',
                                Units),
         SpatialScale = if_else(Covariate == 'S2_02_11',
                                'Reach-2km',
                                SpatialScale)) %>%
  left_join(model_svy_df$mod_full[[1]] %>%
              summary() %>%
              coefficients() %>%
              as_tibble(rownames = "Covariate") %>%
              select(1:3)) %>%
  select(-Covariate) %>%
  rename(`Spatial Scale` = SpatialScale,
         Covariate = Name) %>%
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile random forest (QRF) model predictions of spring/summer-run Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.",
        booktabs = T,
        linesep = "", 
        escape = F,
        digits = 3) %>%
  kable_styling(latex_options = c("hold_position"))

@@

```{r extrap-r2-table, eval = T}
model_svy_df %>%
  ungroup() %>%
  mutate(n_full = map_dbl(data,
                          .f = nrow),
         k_full = map_dbl(mod_full,
                          .f = function(x) {
                            names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                              length
                          }),
         r_full = map_dbl(mod_full,
                          .f = function(x) {
                            cor(x$y, x$fitted.values)
                          }),
         r2_full = r_full^2,
         r2_adj_full = 1 - ( ( (1 - r2_full) * (n_full - 1) ) / (n_full - k_full - 1) )) %>%
  mutate(n_no_champ = map_dbl(data,
                              .f = nrow),
         k_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                                  length
                              }),
         r_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                cor(x$y, x$fitted.values)
                              }),
         r2_no_champ = r_no_champ^2,
         r2_adj_no_champ = 1 - ( ( (1 - r2_no_champ) * (n_no_champ - 1) ) / (n_no_champ - k_no_champ - 1) )) %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  filter(response == "fish/m") %>%
  select(Model = model,
         Response = response,
         `$r^2$` = R2, 
         `Adjusted $r^2$` = `Adjusted R2`) %>%
  kable(caption = "Summary of extrapolation model fits, split by whether the extrapolation model used CHaMP watershed as a covariate or not.",
        escape = F,
        booktabs = T,
        linesep = "",
        digits = 3) %>%
  kable_styling(latex_options = c("hold_position"))

@@

```{r sr-table, eval = T}
spawn_rec_params %>%
  select(Population, data) %>%
  unnest(data) %>%
  group_by(Population) %>%
  summarise(`n Yrs` = n_distinct(BroodYear),
            Spawner_type = unique(Spawner_type)) %>%
  select(Population, `n Yrs`, Spawner_type) %>%
  mutate(Spawner_type = recode(Spawner_type,
                               'total spawners' = 'Spawners',
                               'redd counts' = 'Redds')) %>%
  rename(`Adult Data` = Spawner_type) %>%
  mutate(`Parr Data` = if_else(grepl('Chiwawa', Population),
                               'Parr Surveys',
                               'RST')) %>%
  full_join(spawn_rec_params %>%
              mutate(prnt_val = paste0(prettyNum(round(est), big.mark = ','), ' (', round(cv, 3), ')')) %>%
              select(Population, form, prnt_val) %>%
              mutate(form = recode(form,
                                   'BevertonHolt' = 'Beverton Holt',
                                   'Hockey' = 'Hockey Stick')) %>%
              mutate(form = factor(form,
                                   levels = c('Beverton Holt',
                                              'Ricker',
                                              'Hockey Stick',
                                              'QRF'))) %>%
              spread(form, prnt_val)) %>%
  filter(Population %in% keep_wtsds) %>%
  mutate(Population = recode(Population,
                             'Chiwawa R.' = 'Chiwawa River')) %>%
  kable(caption = "Estimates of parr capacity from both spawner-recruit data (Beverton-Holt, Ricker, hockey stick) and from extrapolated estimates of parr capacity from the quantile random forest (QRF) model. Numbers in parentheses are coefficients of variation.",
        booktabs = T,
        linesep = "") %>%
  kable_styling(latex_options = c("hold_position")) %>%
  # kable_styling(latex_options = c('scale_down')) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(5:8), width = "0.5in")

@@

```{r pdp-figure, fig.height = 6, fig.cap = "Partial dependence plots for the spring/summer-run Chinook salmon parr capacity quantile random forest (QRF) model, depicting how parr capacity shifts as each habitat metric changes, assuming all other habitat metrics remain at their mean values. Tick marks along the X-axis depict observed values."}
plot_partial_dependence(rf_mod = qrf_mod,
                        data = qrf_data,
                        data_dict = hab_dict %>%
                          select(-Name) %>%
                          inner_join(sel_hab_mets %>%
                                       select(ShortName = Metric,
                                              Name)),
                        type = 'quantile',
                        pred_quantile = 0.9,
                        log_transform = T,
                        log_offset = dens_offset,
                        scales = 'free') +
  labs(y = 'Capacity Prediction (per m)') +
  scale_color_grey(start = 0.5, end = 0.5) +
  theme(legend.position = 'none',
        strip.text = element_text(size = 10),
        axis.text = element_text(size = 8))
```

@@

spawn_rec_comp_p +
  theme(strip.text = element_text(size = 10),
        axis.text = element_text(size = 8))
```

>>>>

---
title: "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    bookdown::word_document2:
      fig_caption: yes
      # reference_docx: "../templates/EcologicalApplicationsTemplate.docx" # Insert path for the DOCX file
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: false
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      number_sections: false
      toc: no
      fig_width: 7
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      number_sections: false
      toc: no
      geometry: margin=1in
      latex_engine: "xelatex"
      keep_tex: true
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
      includes:
        in_header: ../templates/header_manuscript.tex
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
abstract: |
  Establishing robust methods and metrics to evaluate habitat quality is critical for the recovery of endangered Pacific salmonids. A variety of modeling approaches are used for status and trend monitoring of anadromous species throughout the Pacific Northwest, USA, but current methods may fail to capture the complex relationship between fish and habitat and are often limited in predictive power beyond specific watersheds. Further, the focus on species distribution and abundance is not easily manipulated to predict carrying capacity and traditional stock-recruitment analyses are reliant on long-term data which are not always available. In this study, we developed a quantile random forest (QRF) model to  provide estimates of habitat carrying capacity for Chinook salmon parr during the summer months, at both the site and watershed scale. QRF models allow for the consideration of noisy data, correlated variables, and non-linear relationships: common features in fish-habitat datasets. We leveraged Columbia Habitat Monitoring Program (CHaMP) data to select habitat co-variates and predict capacity at those sites. We also identified a set of globally available attributes to extrapolate capacity estimate predictions throughout wadeable streams within the Columbia River basin. Total capacity estimates for watersheds closely matched estimates from alternative fish productivity models. Carrying capacity estimates based on QRF, like those presented here, provide managers a framework to guide the identification, prioritization, and development of habitat rehabilitation actions to recover salmon populations.
keywords: |
  carrying capacity; Chinook salmon; quantile random forest; quantile regression; random forests
highlights: |
  These are the highlights. 
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("pdf", "png", "tiff"),
  dpi = 400
)
```

@@

Most studies that have investigated fish-habitat relationships focus on predicting a species’ distribution (presence/absence) or the average abundance or density: neither of which can be easily manipulated to predict carrying capacity. Further, many of these studies focus on only one or two measures of habitat. @Fausch1988 conducted a thorough review of attempts to predict the abundance of fish from measurable habitat covariates from 1950 to 1985 and found that the vast majority of multiple linear regression models failed to detect a significant fish-habitat signal. Since that review, there has been progress in identifying some fish-habitat relationships for several salmonid species. @Nickelson1992 demonstrated that juvenile coho salmon (*O. kisutch*) were found in higher densities within pool habitat on the Oregon coast. Similarly, pool and pond densities were good predictors of coho smolt densities in western Washington [@Sharma2001]. @Bryant2009 found that juvenile coho abundance was positively related to large wood at the reach scale; however their results demonstrated a negative relationship between abundance and the number of pools. @Braun2011 similarly found positive associations between spawner densities of sockeye salmon (*O. nerka*) in the Fraser River and large wood, in addition to positive relationships to percent undercuts and percent pools. Densities of adult spawning coho were also higher in forested areas compared to urban or agricultural areas in the Snohomish River watershed [@Pess2002]. @Mossop2006 examined juvenile Chinook salmon (*O. tshawytscha*) in the Yukon River and found positive correlations between the log of fish density and several metrics related to residual pool dimensions and large woody debris abundance as well as a negative correlation between fish density and gradient. These studies were focused on predicting observed fish densities, not necessarily capacity, and for most of them the predictive extent is limited to a particular watershed. In addition, they all assumed some form of linear fish-habitat relationship which often results in weak predictive power.

@@

```{r fish-hab-sites}
qrf_data %>%
  tabyl(Watershed) %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  rename(`n Sites` = n,
         Percent = percent) %>%
  kable(caption = 'The number of unique sites, by watershed, with paired fish-habitat data used to populate the spring/summer-run Chinook salmon parr capacity QRF model',
        booktabs = T,
        linesep = "") %>%
  kable_styling(font_size = 10,
                latex_options = c("hold_position"))

@@

```{r select-mets-table, eval = T}
qrf_mod$importance %>%
  as_tibble(rownames = 'ShortName') %>%
  rename(imp = IncNodePurity) %>%
  arrange(desc(imp)) %>%
  mutate(Rank = 1:n()) %>%
  select(-imp) %>%
  left_join(hab_dict %>%
              select(-Name) %>%
              inner_join(sel_hab_mets %>%
                           rename(ShortName = Metric)) %>%
              mutate(Name = str_replace(Name, '\n', ' '))) %>%
  filter(MetricGroupName != 'Tier 1 Summary') %>%
  select(Rank,
         Metric = Name,
         `Metric Category` = MetricCategory,
         Description = DescriptiveText) %>%
  kable(caption = "Habitat metrics and descriptions of metrics included in the QRF model to predict spring/summer-run Chinook salmon parr capacity. Metrics are ranked in order of relative importance.",
        booktabs = T,
        linesep = "",
        format.args = list(width = c(2, 10, 10, 50))) %>%
  kable_styling(font_size = 10,
                latex_options = c("hold_position")) %>%
  column_spec(4, width = '3in')

@@

```{r gaa-covars, eval = T}
tibble(Covariate = gaa_covars) %>%
  left_join(gaa_meta %>%
              select(Covariate = FieldName,
                     Name = DisplayName,
                     Units,
                     SpatialScale)) %>%
  mutate(Units = if_else(Units == "na",
                         as.character(NA),
                         Units),
         Units = if_else(grepl('\\^2', Units),
                         str_replace(Units, '\\^2', '$^2$'),
                         Units)) %>%
  mutate(Name = if_else(Covariate == 'S2_02_11' & is.na(Name),
                        'NorWeST Aug. Temperature',
                        Name),
         Units = if_else(Covariate == 'S2_02_11',
                                'C',
                                Units),
         SpatialScale = if_else(Covariate == 'S2_02_11',
                                'Reach-2km',
                                SpatialScale)) %>%
  left_join(model_svy_df$mod_full[[1]] %>%
              summary() %>%
              coefficients() %>%
              as_tibble(rownames = "Covariate") %>%
              select(1:3)) %>%
  select(-Covariate) %>%
  rename(`Spatial Scale` = SpatialScale,
         Covariate = Name) %>%
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile random forest (QRF) model predictions of spring/summer-run Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.",
        booktabs = T,
        linesep = "", 
        escape = F,
        digits = 3) %>%
  kable_styling(font_size = 10,
                latex_options = c("hold_position"))

@@

```{r extrap-r2-table, eval = T}
model_svy_df %>%
  ungroup() %>%
  mutate(n_full = map_dbl(data,
                          .f = nrow),
         k_full = map_dbl(mod_full,
                          .f = function(x) {
                            names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                              length
                          }),
         r_full = map_dbl(mod_full,
                          .f = function(x) {
                            cor(x$y, x$fitted.values)
                          }),
         r2_full = r_full^2,
         r2_adj_full = 1 - ( ( (1 - r2_full) * (n_full - 1) ) / (n_full - k_full - 1) )) %>%
  mutate(n_no_champ = map_dbl(data,
                              .f = nrow),
         k_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                                  length
                              }),
         r_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                cor(x$y, x$fitted.values)
                              }),
         r2_no_champ = r_no_champ^2,
         r2_adj_no_champ = 1 - ( ( (1 - r2_no_champ) * (n_no_champ - 1) ) / (n_no_champ - k_no_champ - 1) )) %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  filter(response == "fish/m") %>%
  select(Model = model,
         Response = response,
         `$r^2$` = R2, 
         `Adjusted $r^2$` = `Adjusted R2`) %>%
  kable(caption = "Summary of extrapolation model fits, split by whether the extrapolation model used CHaMP watershed as a covariate or not.",
        escape = F,
        booktabs = T,
        linesep = "",
        digits = 3) %>%
  kable_styling(font_size = 10,
                latex_options = c("hold_position"))

@@

```{r sr-table, eval = T}
spawn_rec_params %>%
  select(Population, data) %>%
  unnest(data) %>%
  group_by(Population) %>%
  summarise(`n Yrs` = n_distinct(BroodYear),
            Spawner_type = unique(Spawner_type)) %>%
  select(Population, `n Yrs`, Spawner_type) %>%
  mutate(Spawner_type = recode(Spawner_type,
                               'total spawners' = 'Spawners',
                               'redd counts' = 'Redds')) %>%
  rename(`Adult Data` = Spawner_type) %>%
  mutate(`Parr Data` = if_else(grepl('Chiwawa', Population),
                               'Parr Surveys',
                               'RST')) %>%
  full_join(spawn_rec_params %>%
              mutate(prnt_val = paste0(prettyNum(round(est), big.mark = ','), ' (', round(cv, 3), ')')) %>%
              select(Population, form, prnt_val) %>%
              mutate(form = recode(form,
                                   'BevertonHolt' = 'Beverton Holt',
                                   'Hockey' = 'Hockey Stick')) %>%
              mutate(form = factor(form,
                                   levels = c('Beverton Holt',
                                              'Ricker',
                                              'Hockey Stick',
                                              'QRF'))) %>%
              spread(form, prnt_val)) %>%
  filter(Population %in% keep_wtsds) %>%
  mutate(Population = recode(Population,
                             'Chiwawa R.' = 'Chiwawa River')) %>%
  kable(caption = "Estimates of parr capacity from both spawner-recruit data (Beverton-Holt, Ricker, hockey stick) and from extrapolated estimates of parr capacity from the quantile random forest (QRF) model. Numbers in parentheses are coefficients of variation.",
        booktabs = T,
        linesep = "") %>%
  kable_styling(font_size = 10,
                latex_options = c("hold_position")) %>%
  # kable_styling(latex_options = c('scale_down')) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(5:8), width = "0.5in")

@@

```{r pdp-figure, fig.height = 6, fig.cap = "Partial dependence plots for the spring/summer-run Chinook salmon parr capacity quantile random forest (QRF) model, depicting how parr capacity shifts as each habitat metric changes, assuming all other habitat metrics remain at their mean values. Tick marks along the X-axis depict observed values."}
plot_partial_dependence(rf_mod = qrf_mod,
                        data = qrf_data,
                        data_dict = hab_dict %>%
                          select(-Name) %>%
                          inner_join(sel_hab_mets %>%
                                       select(ShortName = Metric,
                                              Name)),
                        type = 'quantile',
                        pred_quantile = 0.9,
                        log_transform = T,
                        log_offset = dens_offset,
                        scales = 'free') +
  labs(y = 'Capacity Prediction (per m)') +
  scale_color_grey(start = 0.5, end = 0.5) +
  theme(legend.position = 'none',
        strip.text = element_text(size = 9),
        axis.text = element_text(size = 8))
```

@@

spawn_rec_comp_p +
  theme(strip.text = element_text(size = 9),
        axis.text = element_text(size = 8))
```
